%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Senior Member Of Technical Staff} % Job title
    {VMware} % Organization
    {Bengaluru, India} % Location
    {July. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Leading the efforts for metrics pipeline for Pulse IoT Center}
        \item {Built highly scalable microservices for metrics and notifications using http, http/2 and gRPC protocol.}
        \item {Built metrics pipeline which can handle 10k RPS for metrics insights and alerting using influxDB and kapacitor.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer 3} % Job title
    {Xamcheck} % Organization
    {Bengaluru, India} % Location
    {May. 2017 - July. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead Engineer for projects related to CRM, Exams, Feedback and Remedials.}
        \item {Worked on domain designing, architecture and implementation of various projects.}
        \item {Worked on implementation of distributed systems for various long running tasks. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer 2} % Job title
    {Xamcheck} % Organization
    {Bengaluru, India} % Location
    {Oct. 2016 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented RESTful API server in Java/Python for IMAX. A B2B platform used by schools for data driven personalised learning}
        \item {Built and deployed overall service infrastructure several AWS stack(Including EC2, RDS, S3, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Developed API server for teacher and parent apps. Teacher app is used by teacher for teaching, conducting class tests, remedials, attendance, etc. Parent app is used by parents to track the daily school updates of their child.}
        \item {Developed an application in Python which analyzes student performance and generates remedials based on their performance in each topics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer 2} % Job title
    {Ola} % Organization
    {Bengaluru, India} % Location
    {Feb. 2015 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer for Ola Care backend system in Java, that can discover customer queries and give one click solutions for their problems.}
        \item {Designed and implemented Mirage, an application which renders rides specific route images used in the various section of the app and invoices.}
        \item {Implemented authentication and authorisation functionality in Java for customer support team for various applications based on roles and permissions.}
        \item {Implemented Issue Tracking System which created tickets based on issue and auto assigned it.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Goibibo(Ibibo Group)} % Organization
    {Bengaluru, India} % Location
    {March. 2014 - Feb. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementation of fare calendars for international flights which helps the customers to choose the cheapest option.}
        \item {Integration of SOAP API and parsing their response for various GDS.}
        \item {Improved response time of search, reprice and bookings for airline e-tickets.}
        \item {Implemented an in-house CRM system for support team using Python/Django.}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Associate Software Engineer} % Job title
    {Apostek Softwares} % Organization
    {Bengaluru, India} % Location
    {Jun. 2013 - March. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {To develop application using Java and Python to manage the business logs for Web Application and Mobile Apps.}
        \item {Analyze the data to give a graphical view in form of charts which helps in business decisions.}
      \end{cvitems}
    }
\end{cventries}
